Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-11-24 main.tex
:pencil: Summarize energy detection

		\begin{subsection}{Backscatter Modulation}
			Backscatter modulation is achieved by switching the tag load impedance between different states. For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $\bar{c}_m$ as \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha \frac{\bar{c}_m}{\max_{m'} \lvert \bar{c}_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction. For simplicity, we consider an $M$-ary Phase Shift Keying (PSK) with constellation set $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$, where the $m$-th constellation point is
			\begin{equation}
				\bar{c}_m = \exp \left(j \frac{2 \pi m}{M}\right).
				\label{eq:mpsk}
			\end{equation}
			% Also, define the $M$-PSK constellation set as $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$.

@@

		\begin{subsection}{Signal Detection}
			To reveal the impact of backscatter modulation on the primary transmission, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty. It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.

@@

			% where $\Gamma(\cdot)$ is the gamma function. As such, the equivalent discrete memoryless channel can be defined by a transition matrix from $\mathcal{M^K}$ to $\mathcal{M^K}$,\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.} where the probability of observing output state $j$ under input state $i$ is
			where $\Gamma(\cdot)$ is the gamma function. As such, the equivalent discrete memoryless channel can be defined by a transition matrix where the probability of observing output state $j \in \mathcal{M^K}$ under input state $i \in \mathcal{M^K}$ is\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.}

@@

			In summary, for every candidate backscatter symbol vector, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to the nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the channel transition matrix can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:transition_probability}.

			% the expected power of the received signal per block under all backscatter combinations can be estimated by \eqref{eq:receive_variance}, the energy detection threshold between any backscatter symbol vectors with adjacent

			% can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.

			% estimated at the user.

			% To enable energy detection

			% For the ease of notation, we label the backscatter symbol vector by a decimal number that uniquely maps to the modulation index set. As an example, when tag $k$ is at state $m_k$, the modulation index set is $\{m_1,\ldots,m_K\}$, and the backscatter symbol vector can be defined as $\boldsymbol{c}_l \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T$, where $l \in \{1,\ldots,M^K\}$ in decimal equals $m_1 - 1 \ldots m_{K-1} - 1 \ m_K$ in base-$M$.

			% $\forall k \in \mathcal{K}$, the backscatter symbol vector is $\boldsymbol{c}_l$, where $l$

			% assign the backscatter symbol vector to the corresponding modulation index set, and further label it by the corresponding base-$M$ number.

			% we label the modulation index set $\{m_1,\ldots,m_K\}$ by the corresponding base-$M$ number

			% define the modulation index set as $\{m_1,\ldots,m_K\}$
			% For any backscatter symbol vector $\boldsymbol{c}_l$, the received signal at block $n$ is only subject to the variation of the primary symbol $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution as

			% Since the status of all tags remain unchanged over $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary symbol $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution. When the backscatter symbol vector is $\boldsymbol{c}_l$,
			% Since the status of all tags remain unchanged over $N$ primary symbols, the received signal is only subject to the variation of the primary source and AWGN. When the backscatter symbol vector is $\boldsymbol{c}_l$, the received signal at block $n$ follows CSCG distribution as
			% \begin{equation}
			% 	y_l[n] \sim \mathcal{CN}\biggl(0,\sigma_l^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2\biggr).
			% \end{equation}

			% , and thus follows CSCG distribution. When the backscatter symbol vector is $\boldsymbol{c}_l$,

			% any backscatter symbol vector

			% , and thus follows CSCG distribution as

			% the received

			how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$. In such case, the detection indeed coincides with that of Ambient Backscatter Communications (AmBC) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where

>>>>

		\begin{subsection}{Backscatter Modulation}
			Backscatter modulation is achieved by switching the tag load impedance between different states. For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $\bar{c}_m$ as \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha \frac{\bar{c}_m}{\max_{m'} \lvert \bar{c}_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction. For simplicity, we consider an $M$-ary Phase Shift Keying (PSK) with constellation set $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$, where the $m$-th constellation point is
			\begin{equation}
				\bar{c}_m = \exp \left(j \frac{2 \pi m}{M}\right).
				\label{eq:mpsk}
			\end{equation}

@@

		\begin{subsection}{Backscatter Detection}
			To reveal the impact of backscatter modulation on the primary transmission, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty. It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.

@@

			where $\Gamma(\cdot)$ is the gamma function. As such, the equivalent discrete memoryless channel can be defined by a transition matrix where the probability of observing output $j \in \mathcal{M^K}$ under input $i \in \mathcal{M^K}$ is\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.}

@@

			In summary, for every candidate backscatter symbol vector, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the channel transition matrix can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:transition_probability}.
